---
title: "report 10"
author: "Tara Boroushaki 93105501"
date: "7/12/2018"
output: html_document
---

## Libraries
```{r,warning=F,message=F}
library(readr)
library(dplyr)
library(highcharter)
library(ggplot2)
library(ngram)
library(tidyr)
setwd("/Users/Apple/Documents/TaraFiles/University/term 8/Data Analysis/week_10/hw_10/")
```
***


# 1.
Ten poorest countries are found by their GDP per capita (current US$)". The percentages of poor people are found by "Poverty headcount ratio at 3.20 a day (2011 PPP) (% of population)". 

```{r,warning=F,message=F}

WDICountry_Series=read_csv("./WDI_csv/WDICountry-Series.csv")
WDICountry=read_csv("./WDI_csv/WDICountry.csv")
WDIData=read_csv("./WDI_csv/WDIData.csv")
WDIFootNote=read_csv("./WDI_csv/WDIFootNote.csv")
WDISeries_Time=read_csv("./WDI_csv/WDISeries-Time.csv")
WDISeries=read_csv("./WDI_csv/WDISeries.csv")


WDIData$`Indicator Name`%>%unique()%>%as.data.frame()->a

WDIData%>%filter(`Indicator Name`=="GDP per capita (current US$)" |
                   `Indicator Name`=="Poverty headcount ratio at $3.20 a day (2011 PPP) (% of population)" |
                   `Indicator Name`=="Poverty headcount ratio at $3.20 a day (2011 PPP) (% of population)") %>%
  select(`Country Name`,`Country Code`,`2011`,`Indicator Name`) -> WDIData_q1



WDIData_q1%>%filter(`Indicator Name`=="GDP per capita (current US$)")%>%arrange(`2011`)%>%head(n=10L)

WDIData_q1%>%filter(`Indicator Name`=="GDP per capita (current US$)")%>%arrange(`2011`)%>%
  select(`Country Name`)%>% .[1:10,] ->poorCOUNTRYcode

WDIData%>%filter(`Country Name` %in% poorCOUNTRYcode$`Country Name`)%>%
  filter(`Indicator Name`=="Poverty headcount ratio at national poverty lines (% of population)")%>%
  select(`Country Name`,`2008`,`2010`,`2011`,`2012`,`2014`)->Q1_poverty

MEAN=c(Q1_poverty[1,6],Q1_poverty[2,2],Q1_poverty[3,5],Q1_poverty[4,3],
       Q1_poverty[5,3],Q1_poverty[6,6],Q1_poverty[7,5],Q1_poverty[8,3],
       Q1_poverty[9,4],Q1_poverty[10,4])
Q1_poverty$value=as.numeric(MEAN)
Q1_poverty=Q1_poverty%>%select(`Country Name`,value)%>%mutate(type="poor percent")

WDIData%>%filter(`Country Name` %in% poorCOUNTRYcode$`Country Name`)%>%
  filter(`Indicator Name`=="Life expectancy at birth, total (years)")%>%
  select(`Country Name`,value=`2011`)%>%mutate(type="life_expectancy")->Q1_life


WDIData%>%filter(`Country Name` %in% poorCOUNTRYcode$`Country Name`)%>%
  filter(`Indicator Name`=="Adjusted net national income per capita (current US$)")%>%
  select(`Country Name`,value=`2011`)%>%mutate(type="AVGincome")->Q1_income

rbind(Q1_income,Q1_life,Q1_poverty)->q1



p1=ggplot(q1,aes(x=`Country Name`,y=value))+geom_bar(aes(fill = type),stat = "identity",position = "dodge",linetype = "dashed",color = "red",alpha=0.5)+
  xlab("country name")+ylab("value")+ggtitle("Q1")+theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
p1

```
***

# 2.
The Rwandan genocide, also known as the genocide against the Tutsi, was a genocidal mass slaughter of Tutsi in Rwanda by members of the Hutu majority government. An estimated 500,000 to 1,000,000 Rwandans were killed during the 100-day period from 7 April to mid-July 1994,constituting as many as 70% of the Tutsi population.
(from wikipedia)

```{r,warning=F,message=F}
WDIData%>%filter(`Indicator Name`=="Life expectancy at birth, total (years)")->q2_life
q2_life=q2_life[,-c(1,3,4)]
q2_life=q2_life[,c(1,33:47)]%>%na.omit()

q2_life%>%filter(`Country Code`=="RWA")->RWA

RWA[,-1]%>%as.numeric()->RWA_pop
year=as.character(c(1991:2005))
data.frame(pop=RWA_pop,year=as.character(year))->RWA_data

rbind(q2_life%>%select(pop=`1991`)%>%mutate(year="1991"),
    q2_life%>%select(pop=`1992`)%>%mutate(year="1992"),
    q2_life%>%select(pop=`1993`)%>%mutate(year="1993"),
    q2_life%>%select(pop=`1994`)%>%mutate(year="1994"),
    q2_life%>%select(pop=`1995`)%>%mutate(year="1995"),
    q2_life%>%select(pop=`1996`)%>%mutate(year="1996"),
    q2_life%>%select(pop=`1997`)%>%mutate(year="1997"),
    q2_life%>%select(pop=`1998`)%>%mutate(year="1998"),
    q2_life%>%select(pop=`1999`)%>%mutate(year="1999"),
    q2_life%>%select(pop=`2000`)%>%mutate(year="2000"),
    q2_life%>%select(pop=`2001`)%>%mutate(year="2001"),
    q2_life%>%select(pop=`2002`)%>%mutate(year="2002"),
    q2_life%>%select(pop=`2003`)%>%mutate(year="2003"),
    q2_life%>%select(pop=`2004`)%>%mutate(year="2004"),
    q2_life%>%select(pop=`2005`)%>%mutate(year="2005"))->q2_life_box

hcboxplot(x = q2_life_box$pop, var = q2_life_box$year,outliers=F)%>%
  hc_add_series(RWA_data, "spline", hcaes(y = pop,x=year), name = "Rwanda")%>%
  hc_title(text="Rwanda Vs other countries")
  
```

***

# 3.
When countries are sorted by their life expectancy in 2011, their health expenditure per capita has a decreasing trend. The higher the health expenditure per capita, the higher is their life expectancy.

```{r,warning=F,message=F}
# Q3

WDIData%>%filter(`Indicator Name`=="Life expectancy at birth, total (years)")%>%
  select(`Country Name`,valueL=`2011`)->Q3_life

WDIData%>%filter(`Indicator Name`=="Current health expenditure per capita (current US$)")%>%
  select(`Country Name`,valueH=`2011`)->Q3_health
Q3_health$valueH=Q3_health$valueH/100

full_join(Q3_life,Q3_health,by="Country Name")%>%na.omit()%>%
  arrange(-valueL)%>%mutate(num=row_number())->Q3

rbind(Q3%>%select(num,value=valueH)%>%mutate(type="health expenditure in 100$"),
      Q3%>%select(num,value=valueL)%>%mutate(type="Life expectancy"))->Q3_plot


p3=ggplot(Q3_plot,aes(x=num,y=value))+geom_smooth(aes(color =type))+
  xlab("country")+ylab("value")+ggtitle("Q3")+theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
p3

```
***

# 4.
Roughly speaking, there has been an increasing trend in the last 50 years. However in the last 10 years it has generally decreased.

```{r,warning=F,message=F}
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep.")%>%
  filter(`Indicator Name`=="Household final consumption expenditure per capita (constant 2010 US$)")->ir_h

ir_h=ir_h[,-c(1:4)]

data.frame(power=as.numeric(ir_h[-c(58,59)]),year=c(1960:2016))->q4

p4=ggplot(q4,aes(x=year,y=power))+geom_line()+
  xlab("year")+ylab("Household final consumption expenditure per capita")+ggtitle("Q4")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
p4
```

# 5.

```{r,warning=F,message=F}

a[sort(c(624,328,1546,1551,195,684,522,515,1060,573,677,71,517,511,69,616, 691 ,935)),]->index

as.data.frame(index)->index
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep." )%>%
  filter(`Indicator Name`%in%index$index)%>%arrange(`Indicator Name`)->iran

WDIData%>%filter(`Country Name`=="World")%>%
  filter(`Indicator Name`%in%index$index)%>%arrange(`Indicator Name`)->WLD


WDIData%>%filter(`Country Name`=="Iran, Islamic Rep." | `Country Name`=="World")%>%
  filter(`Indicator Name`=="GDP per capita (constant 2010 US$)")->GDP

iran_GDP=data.frame(data=as.numeric(GDP[2,5:62]),year=1960:2017)
iran_GDP$data=iran_GDP$data/1000
WLD_GDP=data.frame(data=as.numeric(GDP[1,5:62]),year=1960:2017)
WLD_GDP$data=WLD_GDP$data/1000

lst1 = list()

for (i in 1:18) {
  
  data.frame(value=as.numeric(iran[i,5:62]),year=1960:2017)->x
  data.frame(value=as.numeric(WLD[i,5:62]),year=1960:2017)->x1
  hchart(x,"line", hcaes(y = value, x = year),name= concatenate("IRR ",as.character(iran[i,3])))%>%
    hc_add_series(x1, "spline", hcaes(y = value, x = year), name = concatenate("WLD ",as.character(iran[i,3])))%>%
    hc_title(text =as.character(iran[i,3]))%>%
    hc_add_theme(hc_theme_sandsignika())->hc1
  lst1[[i]] <- hc1
}

hchart(iran_GDP, "spline", hcaes(y = data, x = year), name = "IRR GDP per capita in 1000$")%>%
  hc_add_series(WLD_GDP, "spline", hcaes(y = data, x = year), name = "WLD GDP per capita in 1000$")%>%
  hc_title(text ="GDP")%>%
  hc_add_theme(hc_theme_sandsignika())->hc1

lst1[[19]] <- hc1
  
htmltools::tagList(lst1)
  
```


# 6.

```{r,fig.width=13,fig.height=13,warning=F,message=F}


WDIData%>%filter(`Indicator Name`%in%index$index)%>%arrange(`Country Code`,`Indicator Name`)%>%
  select(code=`Country Code`,data=`2005`,`Indicator Name`)%>%group_by(code)%>%
  mutate(indicator=row_number(code))%>%select(code,indicator,data)->q6

codeList=unique(q6$code)
#264
q6%>%filter(code==codeList[1])%>%arrange(indicator)->x
w=t(as.table(x$data))
for (i in 2:264) {
  q6%>%filter(code==codeList[i])%>%arrange(indicator)->x
  w1=t(as.table(x$data))
  w=rbind(w,w1)
  
  }

w=as.data.frame(w)
Q6_data=cbind(as.data.frame(codeList),w)
Q6_data[111,"N"]=Q6_data[258,"N"]
Q6_data%>%drop_na()->Q6_data
kcl = kmeans(Q6_data[,-1],centers = 3)
kcl
plot(Q6_data,col = kcl$cluster,pch = 20,cex = 2)


Q6=data.frame(name=Q6_data[,1],cluster=kcl$cluster)
ir_cls_num=Q6$cluster[which(as.character(Q6$name)=="IRN")]
Q6%>%filter(cluster==ir_cls_num)->IRN_clus
WDIData%>%filter(`Country Code`%in% IRN_clus$name)%>%select(`Country Name`)%>%unique()->IRN_clus_names

print(IRN_clus_names)

```



# 7.
Most of countries are in one cluster, and only a small portion of them are in other 2. The clustring result is satisfying.

```{r,fig.width=13,fig.height=13,warning=F,message=F}
# Q7

library(ggbiplot)
Q7_pca = prcomp(Q6_data[,-1], scale. = TRUE)
ggbiplot(Q7_pca, obs.scale = 1, var.scale = 1,
         groups =as.character( kcl$cluster), ellipse = TRUE, circle = F) +
  scale_color_discrete(name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')

PCA = Q7_pca$sdev^2

qcc::pareto.chart(PCA)

```
***

# 9. 
Nine comes sooner than eight here!


```{r,fig.width=13,fig.height=13,warning=F,message=F}


iran[,40:62]->ir_Q8
ir_Q8=as.data.frame(t(as.matrix(ir_Q8)))
ir_Q8$growth=iran_GDP[36:58,1]

library(h2o)
h2o.init()

happly = as.h2o(ir_Q8)
hglm = h2o.glm(y = "growth", x= c("V1","V2","V3","V4","V5","V6",
                                  "V7","V8","V9","V10","V11","V12",
                                  "V13","V14","V15","V16","V17","V18"),
               training_frame = happly, family="gaussian")

hglm

```



***
# 8.
Most of countries are in one cluster, and only a small portion of them are in other 2. 

```{r,fig.width=13,fig.height=13,warning=F,message=F}
# Q9
health=a[sort(c(57,139,51,479,332,646,775,1235,1251,1078,1323,1131)),]
edu=a[sort(c(572,574,759,1260,1356,1350,1328,1329,1259,1260,1288,1289,598,599)),]
```

Health related criteria are:
```{r,fig.width=13,fig.height=13,warning=F,message=F}
health
```

Education related criteria are:
```{r,fig.width=13,fig.height=13,warning=F,message=F}
edu
```


```{r,fig.width=13,fig.height=13,warning=F,message=F}
# health

### 5
as.data.frame(health)->health
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep." )%>%
  filter(`Indicator Name`%in%health$health)%>%arrange(`Indicator Name`)->iran

WDIData%>%filter(`Country Name`=="World")%>%
  filter(`Indicator Name`%in%health$health)%>%arrange(`Indicator Name`)->WLD


lst2 = list()

for (i in 1:12) {
  
  data.frame(value=as.numeric(iran[i,5:62]),year=1960:2017)->x
  data.frame(value=as.numeric(WLD[i,5:62]),year=1960:2017)->x1
  hchart(x,"line", hcaes(y = value, x = year),name= concatenate("IRR ",as.character(iran[i,3])))%>%
    hc_add_series(x1, "spline", hcaes(y = value, x = year), name = concatenate("WLD ",as.character(iran[i,3])))%>%
    hc_title(text =as.character(iran[i,3]))%>%
    hc_add_theme(hc_theme_sandsignika())->hc1
  lst2[[i]] <- hc1
}

htmltools::tagList(lst2)


### Q6


WDIData%>%filter(`Indicator Name`%in% health$health)%>%arrange(`Country Code`,`Indicator Name`)%>%
  select(code=`Country Code`,data=`2011`,`Indicator Name`)%>%group_by(code)%>%
  mutate(indicator=row_number(code))%>%select(code,indicator,data)->q6

codeList=unique(q6$code)
#264
q6%>%filter(code==codeList[1])%>%arrange(indicator)->x
w=t(as.table(x$data))
for (i in 2:264) {
  q6%>%filter(code==codeList[i])%>%arrange(indicator)->x
  w1=t(as.table(x$data))
  w=rbind(w,w1)
  
}

w=as.data.frame(w)
Q6_data=cbind(as.data.frame(codeList),w)%>%na.omit()
kcl = kmeans(Q6_data[,-1],centers = 3)
kcl
plot(Q6_data,col = kcl$cluster,pch = 20,cex = 2)

Q6=data.frame(name=Q6_data[,1],cluster=kcl$cluster)
ir_cls_num=Q6$cluster[which(as.character(Q6$name)=="IRN")]
Q6%>%filter(cluster==ir_cls_num)->IRN_clus
WDIData%>%filter(`Country Code`%in% IRN_clus$name)%>%select(`Country Name`)%>%unique()->IRN_clus_names

print(IRN_clus_names)

### Q7
Q7_pca = prcomp(Q6_data[,-1], scale. = TRUE)
ggbiplot(Q7_pca, obs.scale = 1, var.scale = 1,
         groups =as.character( kcl$cluster), ellipse = TRUE, circle = F) +
  scale_color_discrete(name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')

PCA = Q7_pca$sdev^2
#names(PCA) = paste0('PC', eigv$PCs)
qcc::pareto.chart(PCA)

#####################################################################
```




```{r,fig.width=13,fig.height=13,warning=F,message=F}
#####################################################################

# EDU

### 5
as.data.frame(edu)->edu
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep." )%>%
  filter(`Indicator Name`%in%edu$edu)%>%arrange(`Indicator Name`)->iran

WDIData%>%filter(`Country Name`=="World")%>%
  filter(`Indicator Name`%in%edu$edu)%>%arrange(`Indicator Name`)->WLD


lst3 = list()

for (i in 1:13) {
  
  data.frame(value=as.numeric(iran[i,5:62]),year=1960:2017)->x
  data.frame(value=as.numeric(WLD[i,5:62]),year=1960:2017)->x1
  hchart(x,"line", hcaes(y = value, x = year),name= concatenate("IRR ",as.character(iran[i,3])))%>%
    hc_add_series(x1, "spline", hcaes(y = value, x = year), name = concatenate("WLD ",as.character(iran[i,3])))%>%
    hc_title(text =as.character(iran[i,3]))%>%
    hc_add_theme(hc_theme_sandsignika())->hc1
  lst3[[i]] <- hc1
}

htmltools::tagList(lst3)


### Q6


WDIData%>%filter(`Indicator Name`%in% edu$edu)%>%arrange(`Country Code`,`Indicator Name`)%>%
  select(code=`Country Code`,data=`2011`,`Indicator Name`)%>%group_by(code)%>%
  mutate(indicator=row_number(code))%>%select(code,indicator,data)->q6

codeList=unique(q6$code)
#264
q6%>%filter(code==codeList[1])%>%arrange(indicator)->x
w=t(as.table(x$data))
for (i in 2:264) {
  q6%>%filter(code==codeList[i])%>%arrange(indicator)->x
  w1=t(as.table(x$data))
  w=rbind(w,w1)
  
}

w=as.data.frame(w)
Q6_data=cbind(as.data.frame(codeList),w)%>%na.omit()
kcl = kmeans(Q6_data[,-1],centers = 3)
kcl
plot(Q6_data,col = kcl$cluster,pch = 20,cex = 2)

Q6=data.frame(name=Q6_data[,1],cluster=kcl$cluster)
ir_cls_num=Q6$cluster[which(as.character(Q6$name)=="IRN")]
Q6%>%filter(cluster==ir_cls_num)->IRN_clus
WDIData%>%filter(`Country Code`%in% IRN_clus$name)%>%select(`Country Name`)%>%unique()->IRN_clus_names

print(IRN_clus_names)

### Q7
Q7_pca = prcomp(Q6_data[,-1], scale. = TRUE)
ggbiplot(Q7_pca, obs.scale = 1, var.scale = 1,
         groups =as.character( kcl$cluster), ellipse = TRUE, circle = F) +
  scale_color_discrete(name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')

PCA = Q7_pca$sdev^2
#names(PCA) = paste0('PC', eigv$PCs)
qcc::pareto.chart(PCA)

```

***

# 10.

```{r,fig.width=13,fig.height=13,warning=F,message=F}




as.data.frame(c(as.character(health[,1]),as.character(edu[,1]),as.character(index[,1])))%>%unique()->all
names(all)="all"
WDIData%>%filter(`Indicator Name`%in% all$all)%>%arrange(`Country Code`,`Indicator Name`)%>%
  select(code=`Country Code`,data=`2011`,`Indicator Name`)%>%group_by(code)%>%
  mutate(indicator=row_number(code))%>%select(code,indicator,data)->q10

codeList=unique(q10$code)
#264
q10%>%filter(code==codeList[1])%>%arrange(indicator)->x
w=t(as.table(x$data))
for (i in 2:264) {
  q10%>%filter(code==codeList[i])%>%arrange(indicator)->x
  w1=t(as.table(x$data))
  w=rbind(w,w1)
  
}

w=as.data.frame(w)
Q10_data=cbind(as.data.frame(codeList),w)
Q10_data=Q10_data[,-c(25,28)]
Q10_data=Q10_data%>%na.omit()
row.names(Q10_data)=Q10_data$codeList
Q10_data=Q10_data[,-1]
dist = stats::dist(Q10_data,method = "euclidean")
clus = hclust(dist,method = "complete")
plot(clus)
rect.hclust(clus, 3)





```




# 11.

### a.
Prevalence of anemia among children has constantly decresed in iran. it was as high as 50% just 30 years ago, and is  currently less than 30%. Switzerland is one of the ,ost developed and wealthiest countries. Its rate is substantially lower. However, since 2010 the Prevalence of anemia has increased by 3% which is realy odd for such a country!

```{r,fig.width=13,fig.height=13,warning=F,message=F}
#"Prevalence of anemia among children"

WDIData%>%filter(`Country Name`=="Iran, Islamic Rep."  )%>%
  filter(`Indicator Name`==a[1235,])->q11_1_ir
q11_1_ir=data.frame(data=as.numeric(q11_1_ir[,5:62]),year=1960:2017)
WDIData%>%filter(`Country Name`=="Switzerland" )%>%
  filter(`Indicator Name`==a[1235,])->q11_1_ch
q11_1_ch=data.frame(data=as.numeric(q11_1_ch[,5:62]),year=1960:2017)
WDIData%>%filter( `Country Name`=="World" )%>%
  filter(`Indicator Name`==a[1235,])->q11_1_wld
q11_1_wld=data.frame(data=as.numeric(q11_1_wld[,5:62]),year=1960:2017)

hchart(q11_1_ir,"line", hcaes(y = data, x = year),name="IRR")%>%
  hc_add_series(q11_1_wld, "spline", hcaes(y = data, x = year), name ="WLD")%>%
  hc_add_series(q11_1_ch, "spline", hcaes(y = data, x = year), name ="CHF")%>%
  hc_title(text =a[1235,])%>%
  hc_add_theme(hc_theme_sandsignika())


```





### b. 
The immunization against measles rate for Iran is one of the highest. Sunprisingly, the immunization rate for US and switzerland are lower than Iran! I googled it and found that it is not a compulsory vaccination in those two country. In addition to that, there are some debates whether measles vaccine is related to autism in the next generation. 

"Measles vaccination is an important indicator of hesitancy and refusal, since misinformation accusing it of causing autism, despite evidence of its fraudulent source, is still going on. "

If you google the autism rate, it is 1.9% for Iran and 1.7% for US. Due to the fact that there are probably many austism cases in Iran that have not been counted, I wonder whether such speculation about measles vaccine can be proved true in future!


```{r,fig.width=13,fig.height=13,warning=F,message=F}
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep."  )%>%
  filter(`Indicator Name`==a[648,])->q11_2_ir
q11_2_ir=data.frame(data=as.numeric(q11_2_ir[,5:62]),year=1960:2017)
WDIData%>%filter(`Country Name`=="Switzerland" )%>%
  filter(`Indicator Name`==a[648,])->q11_2_ch
q11_2_ch=data.frame(data=as.numeric(q11_2_ch[,5:62]),year=1960:2017)
WDIData%>%filter( `Country Name`=="United States" )%>%
  filter(`Indicator Name`==a[648,])->q11_2_US
q11_2_US=data.frame(data=as.numeric(q11_2_US[,5:62]),year=1960:2017)

hchart(q11_2_ir,"line", hcaes(y = data, x = year),name="IRR")%>%
  hc_add_series(q11_2_US, "spline", hcaes(y = data, x = year), name ="US")%>%
  hc_add_series(q11_2_ch, "spline", hcaes(y = data, x = year), name ="CHF")%>%
  hc_title(text =a[648,])%>%
  hc_add_theme(hc_theme_sandsignika())
```


### c.
Ratio of girls to boys is "gender parity index". Iran's index has the highest growth and is now above 1. US's index has been constantly above 1, but is now a little lower than Iran, I believe such a large growth is a sign of modernization of society in a developing country.

```{r,fig.width=13,fig.height=13,warning=F,message=F}
WDIData%>%filter(`Country Name`=="Iran, Islamic Rep."  )%>%
  filter(`Indicator Name`==a[1356,])->q11_3_ir
q11_3_ir=data.frame(data=as.numeric(q11_3_ir[,5:62]),year=1960:2017)
WDIData%>%filter(`Country Name`=="Switzerland" )%>%
  filter(`Indicator Name`==a[1356,])->q11_3_ch
q11_3_ch=data.frame(data=as.numeric(q11_3_ch[,5:62]),year=1960:2017)
WDIData%>%filter( `Country Name`=="United States" )%>%
  filter(`Indicator Name`==a[1356,])->q11_3_US
q11_3_US=data.frame(data=as.numeric(q11_3_US[,5:62]),year=1960:2017)

hchart(q11_3_ir,"line", hcaes(y = data, x = year),name="IRR")%>%
  hc_add_series(q11_3_US, "spline", hcaes(y = data, x = year), name ="US")%>%
  hc_add_series(q11_3_ch, "spline", hcaes(y = data, x = year), name ="CHF")%>%
  hc_title(text =a[1356,])%>%
  hc_add_theme(hc_theme_sandsignika())




```























